Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-05 writeups/proposal/proposal.tex
foo
Former-commit-id: 77c747083cb5c1981f8f873667c6df5bca5ce545 [formerly 1a3099eb56bb2d31dd595fab9960aeb5a6aacb23]
Former-commit-id: b553b8cc5e91fc0a4be2366279ab8aabb6797d38

With random permutations, each word environment vector ($e_{i}$) is a large sparse vector of zeros with a few $\{1,-1\}$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector ($e_{i}$) is shifted to the left one position ($^{-1}$).
This produces a new environment vector ($e_{i^{-1}}$) for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

For random permutations, each tag is represented by a compressed vector with a length much less than the number of words.
Note that if the length of a word's environment vector was the number of unique words, then each word could be represented by associating it with a particular row in the column vector.
If done in this way, building a matrix of all words' environment vectors by tags would recover the original word by document matrix \parencite{Kanerva2000}.
However, each word's environment vector is compressed using a length much less than the number of unique words and using a combination of a few $\{1,-1\}$s to represent the word.

@@

However, vector-based models and ACT-R's current Bayesian DM model are not identical, and these differences need to be addressed in order to better evaluate the benefits of one over the other.
For example, the frequency and recency of retrievals for each chunk are not currently used for vector-based models when calculating activation.
More recent tweets on a news site like Twitter should be more relevant, for example.
\textcite{Efron2011} tested this claim by evaluating a set of query likelihood models on returning relevant Twitter tweets from search queries.
They showed that a model incorporating recency information of the tweet produced more relevant results than models that did not pay attention to this information.

@@

These models will be the starting point for modeling tag use on the Twitter and StackOverflow sites.
The models may be modified during testing if the data indicate that modifications are needed to improve model performance.
Also there are planned modifications to each model as part of the research:
incorporating user prior information into the vector-based model and incorporating word order information into the Bayesian model.

>>>>

With random permutations, each word environment vector ($e_{i}$) is a large sparse vector of zeros with a few one and negative one values in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector is shifted to the left one position.
This produces a new environment vector ($e_{i^{-1}}$) for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

@@

For random permutations, each tag is represented by a compressed vector with a length much less than the number of words.
Note that if the length of a word's environment vector was the number of unique words, then each word could be represented by associating it with a particular row in the column vector.
If done in this way, building a matrix of all words' environment vectors by tags would recover the original word by document matrix \parencite{Kanerva2000}.
However, each word's environment vector is compressed using a length much less than the number of unique words and represented by using a combination of a few one and negative one values at a unique combination of positions.

@@

Vector-based models and ACT-R's current Bayesian DM model are not identical however, and these differences need to be addressed in order to better evaluate the benefits of one over the other.
For example, the frequency and recency of retrievals for each chunk are not currently used for vector-based models when calculating activation.
More recent tweets on a news site like Twitter should be more relevant, for example.
\textcite{Efron2011} tested this claim by evaluating a set of query likelihood models on returning relevant Twitter tweets from search queries.
They showed that a model incorporating recency information of the tweet produced more relevant results than models that did not pay attention to this information.

@@

These models will be the starting point for modeling tag use on the Twitter and StackOverflow sites.
The models may be modified during testing if the data indicate that modifications will increase the accuracy in which the model's recommended tags agree with the post author's chosen tags.
Also there are planned modifications to each model as part of the research, as these modifications seem likely to improve performance: 
incorporating user prior information into the vector-based model and incorporating word order information into the Bayesian model.
